---
title: "Seoul_Bike"
author: "Hyomin"
date: '2022 4 17 '
output: html_document
---

Data set Source:

Sathishkumar V E, Jangwoo Park, and Yongyun Cho. 'Using data mining techniques for bike sharing demand prediction in metropolitan city.' Computer Communications, Vol.153, pp.353-366, March, 2020
Sathishkumar V E and Yongyun Cho. 'A rule-based model for Seoul Bike sharing demand prediction using weather data' European Journal of Remote Sensing, pp. 1-18, Feb, 2020

Dua, D. and Graff, C. (2019). UCI Machine Learning Repository [http://archive.ics.uci.edu/ml]. Irvine, CA: University of California, School of Information and Computer Science.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data

```{r}
data_frame = read.csv('SeoulBikeData.csv')
# Call data
summary(data_frame)
# data특성 요약 - mean, max, min 등

```

## Check Original Data format
```{r}
head(data_frame)
```

## Plot

```{r}
plot(x=data_frame$Temperature, y= data_frame$Rented.Bike.Count)
```

## Modeling - Linear Regression

```{r}
# y = ax + b (y= bike rent cnt, x = temp -> find best a,b)라는 문제를 푸는 것

linear_regression_model = glm(formula = Rented.Bike.Count ~ Temperature, data = data_frame)

#glm(): find result (a & b)
# save result(a & b) to 'linear_regression_model' 
# Y ~ X : used parameters 

summary(linear_regression_model)

# intercept == b (329.9525)
# Temparature == a (29.0811)
```


## Test this model

```{r}

temp = 23
a = 29.0811
b = 329.9525
y = a*temp + b
y
# Bike rent coutn when temperature is 23 celcius
```

## Prediction Model

```{r}
predict(linear_regression_model, newdata=data.frame(Temperature=c(23)))
```

## Plot the best fit line in red using the derived parameters  
```{r}
plot(x=data_frame$Temperature ,y=data_frame$Rented.Bike.Count)
abline(a=b,b=a, col='red')
# show line
```

## Show several predicted bike counts according to given temperatures
```{r}
temperature_list = c(-10,0,10,20,30,40)
pred_list = predict(linear_regression_model, newdata=data.frame(Temperature=temperature_list))
data.frame(Temperature=temperature_list, Pred_bike_count=pred_list)